Considering scale in multilayer animal social networks

### 2020-06-11 paper/manuscript.Rmd
spat scale

We generated multilayer networks across a series of spatial distance thresholds
for group assignment. Spatial distance thresholds (5, 25, 50, 75, 100, 250 and
500 m) represented a range of visual (short distance) to auditory (long
distance) sensory modalities of caribou. Multilayer networks consisted of the
social association between `r DT[, uniqueN(get(idcol))]` individuals across
three habitat layers (open, forest and forage). At the finest scale, individuals
within 5 m of one another were considered in the same group, whereas at the
coarsest scale, individuals within 500 m of one another were considered in the
same group. We calculated graph strength and multidegree for each habitat layer
and spatial distance threshold, and edge overlap across the entire series of
networks to determine proportion of total edges observed in each combination of
habitat layer and spatial distance threshold.

@@

To assess the influence of spatial scale on multilayer networks, we aggregated
our land cover raster at varying scales <!--relevant to caribou ecology. We
aggregated the 30 m land cover raster using the R package `grainchanger`
[@Graham_2019] at five scales: 100 m, 250 m, 500 m, 750 m and 1000 m. Aggregation
occurred using a modal moving window method using a circular window
corresponding to the above scales [@Graham_2019a]. We assume 30 m and 100 m
represents fine-scale decision making for caribou during foraging, while
re-sampling at 500 m , 750 m and 1000 m represents the scale at which caribou tend to
select and avoid habitat (Bastille-Rousseau et al. 2017).

>>>>

We generated multilayer networks across a series of spatial distance thresholds
for group assignment. Spatial distance thresholds (5, 25, 50, 75, 100, 250 and
500 m) represented a range of visual (short distance) to auditory (long
distance) sensory modalities of caribou. Multilayer networks consisted of the
social association between `r DT[, uniqueN(get(idcol))]` individuals across
three habitat layers (open, forest and forage) for the entire study period. At the finest scale, individuals
within 5 m of one another were considered in the same group, whereas at the
coarsest scale, individuals within 500 m of one another were considered in the
same group. We calculated graph strength and multidegree for each habitat layer
and spatial distance threshold, and edge overlap across the entire series of
networks to determine proportion of total edges observed in each combination of
habitat layer and spatial distance threshold.

@@

To assess the influence of spatial scale, we aggregated our land cover raster at
varying scales relevant to caribou ecology. We aggregated the original 30 m land
cover raster using the R package `grainchanger` [@Graham_2019] across a series
of scales (100 - 1000 m by 100 m steps) The land cover raster was aggregated
using a modal moving window method using a circular window corresponding to the
above scales [@Graham_2019a]. We assume 30 m and 100 m represents fine-scale
decision making for caribou during foraging, while re-sampling at 500 m , 750 m
and 1000 m represents the scale at which caribou tend to select and avoid
habitat (Bastille-Rousseau et al. 2017). For each spatial scale, we generated a
multilayer network consisting of the social association between `r DT[,
uniqueN(get(idcol))]` individuals across three habitat layers (open, forest and
forage) for the entire study period. We calculated graph strength and
multidegree for each habitat layer and spatial scale, and edge overlap across
the entire series of networks to determine proportion of total edges observed in
each combination of habitat layer and spatial scale.
